---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RepertoiR

Visualization platform for T cell receptor repertoire analysis output results.
It includes comparison of sequence frequency among samples, network of similar
sequences and convergent recombination source between species. Currently 
repertoire analysis is in early stage of development and requires new 
approaches for repertoire data examination and assessment as we intend to 
develop.

## Installation

<!-- You can install the released version of RepertoireGraphs from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("RepertoireGraphs") -->
<!-- ``` -->

You can install the development version of RepertoiR from version from GitHub with:

``` r
# install.packages("devtools")
devtools::install_github("systemsbiomed/RepertoiR")
```
## Quick demo

Creating network graph of TCR repertoire's clonotypes:

```{r example}
library(RepertoireGraphs)

aa <- c(
  "G", "A", "V", "L", "I", "P", "F", "Y", "W", "S",
  "T", "N", "Q", "C", "M", "D", "E", "H", "K", "R"
)
data <- matrix(rexp(1 / 2, n = 1000), ncol = 4)
cons <- sample(aa, 10)
aavec <- c()

while (length(aavec) < nrow(data)) {
  aaseq <- cons
  index <- sample(length(aaseq), sample(length(aaseq) / 3, 1))
  aaseq[index] <- sample(aa, length(index), replace = TRUE)
  aaseq <- paste0(aaseq, collapse = "")
  aavec <- unique(append(aavec, aaseq))
}

rownames(data) <- aavec
colnames(data) <- LETTERS[1:ncol(data)]
```


```{r pressure, echo = FALSE}
network(data, by = 3, nrow = 250)
```

