---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RepertoireGraphs

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/IdoHassonJ/RepertoireGraphs.svg?branch=main)](https://travis-ci.com/IdoHassonJ/RepertoireGraphs)
<!-- badges: end -->

The goal of RepertoireGraphs is to...
Repertoire Graphical Visualization

## Installation

For RepertoireGraphs installation execute the following command:

``` r
install.packages("RepertoireGraphs")
```

or

``` r
library(devtools)
devtools::install_github("IdoHassonJ/RepertoireGraphs")
```
## Example

Load the package and create TCR/BCR dataset with arbitrary sequences & values:

```{r example}
library(RepertoireGraphs)
data <- matrix(rexp(400,1/4), ncol = 4)
aa <- c("G", "A", "V", "L", "I", "P", "F", "Y", "W", "S",
        "T", "N", "Q", "C", "M", "D", "E", "H", "K", "R") # amino acid symbols
seq <- replicate(nrow(data), paste0(sample(aa, 10), collapse = ""))
rownames(data) <- seq
colnames(data) <- LETTERS[seq(ncol(data))]

head(data)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/master/examples>.

You can also embed plots, for example:

```{r pressure, echo = FALSE}
plot(pressure)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
