---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RepertoireGraphs

<!-- badges: start -->
[![R-CMD-check](https://github.com/IdoHassonJ/RepertoireGraphs/workflows/R-CMD-check/badge.svg)](https://github.com/IdoHassonJ/RepertoireGraphs/actions)
<!-- badges: end -->

Different methods to visualize your TCR/BCR repertoire output files of various 
formats options, including a comparison of sequence frequency among samples, 
network representation of similar sequences and convergent recombination source 
between species. 

## Installation

<!-- You can install the released version of RepertoireGraphs from [CRAN](https://CRAN.R-project.org) with: -->

<!-- ``` r -->
<!-- install.packages("RepertoireGraphs") -->
<!-- ``` -->

You can install the development version of RepertoireGraphs from version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("IdoHassonJ/RepertoireGraphs")
```
## Quick demo

Creating network graph of TCR repertoire's clonotypes:

```{r example}
library(RepertoireGraphs)

aa <- c(
  "G", "A", "V", "L", "I", "P", "F", "Y", "W", "S",
  "T", "N", "Q", "C", "M", "D", "E", "H", "K", "R"
)
data <- matrix(rexp(1 / 2, n = 1000), ncol = 4)
cons <- sample(aa, 10)
aavec <- c()

while (length(aavec) < nrow(data)) {
  aaseq <- cons
  index <- sample(length(aaseq), sample(length(aaseq) / 3, 1))
  aaseq[index] <- sample(aa, length(index), replace = TRUE)
  aaseq <- paste0(aaseq, collapse = "")
  aavec <- unique(append(aavec, aaseq))
}

rownames(data) <- aavec
colnames(data) <- LETTERS[1:ncol(data)]
```


```{r pressure, echo = FALSE}
network(data, by = 3, nrow = 250)
```

In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
